\section{Project plan and management}
\input{project_management/methodology}

\subsection{Group organization}
The group strives to have a flat organizational structure, where each role has distinct responsibilities, but no role is more important than any other role. In this section, we will talk about each role, what the responsibilities are for this role, and how these roles are distributed between the group members.

\subsubsection{Roles}
\paragraph{\textbf{Scrum master}}
The Scrum Master, also known as the Project Manager is responsible for keeping track of the groups progress, manage workload, contact with the customer and advisor, and responsible for the weekly status reports.

The scrum master is also responsible for booking rooms for meetings, preparing meeting agendas and managing each meeting.

\paragraph{\textbf{Technical responsible}}
The Technical responsible is responsible for the version control system, training of other group members, making scripts for batch jobs, like creating timetables, and being an advisor in technical matters to the Scrum Master.

\paragraph{\textbf{Test leader}}
The Test leader is responsible for creating and making sure tests are run. The test responsible should create standards for testing, such as unit tests, make sure the unit tests are up to date, and covers an adequate amount of functionality. He is also responsible for creating integration tests, usability tests and any other tests deemed necessary for the completion of the project.

\paragraph{\textbf{Development responsible}}
The development responsible is responsible for code standards, code conventions, code quality and the development team. The development responsible will do code reviews and manage the progress of the application development.

\paragraph{\textbf{Documentation responsible}}
The documentation responsible is responsible for the quality of documentation, and keeping the documentation up-to-date with the development. In addition, the development responsible is required to have an overview of the entire document, how it is structured, and maintaining a steady progress.

\paragraph{\textbf{Product owner}}
The product owner is not part of the group. He is a representative of the customer responsible for taking decisions regarding the product, should there be any questions. He has final word in all decisions.

\subsubsection{Role allocation}
Each role allocation is dynamic throughout the entire project. Any member of the group can change his role if he desires another responsibility during the project. In addition, some roles have dynamic responsibilities, such that the technical responsible can do testing, and the testing responsible can do coding. This is in conform with the agile methodology, SCRUM.

However, the role of technical responsible and scrum master will remain throughout the project to ease contact with the product owner and advisor at IDI. These two roles are also the most dynamic, and can do the work of other roles if deemed necessary.

Each role has been allocated through internal group meetings by majority vote. Dag-Inge Aas is Scrum Master, Stian Liknes is Technical responsible and Test leader. Andreas Skomedal is development responsible and Yonathan Redda is documentation responsible. In addition, Askild Olsen is the product owner.
