\subsection{Quality assurance}

This section contains routines that should be followed to ensure the
quality of the product and its report. In a bid to incorporate quality ensuring
procedures, the group will follow the development tasks in line with
internationally accepted standards recommendations documents such as ISO9126.

\paragraph{ISO9126}
ISO9126 is a document from the international organization for standardization
that recommends software qualities be checked against six core characteristics,
which are described in short below and will be used as reference point for
quality assurance reminders in this project\cite{iso:9126}. 

\begin{itemize}
		\item Functionality - make sure the functionalities are those functionalities that satisfy the stated or implied needs.
		\item Reliability - make sure the software is capable of maintaining its level of performance under a specified condition in a specified period of time.
		\item Usability - the level of effort to use the system and assessment by a stated set of users.
		\item Efficiency - The level of performance versus the amount of resource applied under a specified condition.
        \item Maintainability - The level of effort required to make a specified modifications.
        \item Portability - The ability of the software to be able to be deployed or be transferred from one environment to another.
\end{itemize}

The following is how we chose to implement this standard.

\subsubsection{Templates}
All meeting agendas, meeting minutes and status reports will follow the
templates as shown in Appendix A. These are shared by all group members on
Google Docs. 

\subsubsection{Group dynamics}

All communication will be done in English.
Monday through Thursday every week there will be scrum stand-up at 09.15 at Drivhuset.
Documentation written should be proofread by at least one of the other group members
to assure good grammar and avoid typographical errors.
Every meeting starts with a meeting agenda and notes for the meeting minutes will be
written for all meetings and distributed to the entire group by email in
PDF-form.

All email correspondence within or to external sources will be sent as a CC to
cdproject8@googlegroups.com. This will send a copy to all members of the group.
In addition to this, all documents shared on google docs will also be shared
with this group.

Meeting agendas will be distributed amongst the group 24 hours before the
meeting at the latest. The document will be sent by email in PDF-form. 

\subsubsection{Customer relations and meetings}
There will be a demo for the customer on every customer meeting to let them
know how far along the project is and to catch misunderstandings or direction changes early on.
The customer will receive the meeting minutes after every meeting and approve
them and if there is no response within 48 hours they are regarded as approved.

\subsubsection{Advisor relations and meetings}
There will be a meeting with the Advisor every week, any information that the advisor
should comment on should be submitted to him before 1400 the day prior to the meeting.
On a regular basis this includes: project status, project plan, summary of last weeks
meeting minutes and an hour sheet for group members, this should preferably be
included in one file.
The group number should always be included when contacting the advisor. All
correspondence will be done in English.
