\subsection{Software quality standards}
\subsubsection{ISO 9126 - Quality of use}
The ISO 9126 standard document is a quality assurance recommendation model that evaluates software quality using 6 main characteristics.

\paragraph{Functionality}
This is the essence of having the system and the goals of the system.  Functional requirement definition is relatively easy to define. The functionality of the system can also easily be defined. A system saving an observation is functional and it can practically be tested.

\paragraph{Reliability}
Once a software system is functioning, as specified, and delivered the reliability characteristic defines the capability of the system to maintain its service provision under defined conditions for defined periods of time. One aspect of this characteristic is fault tolerance that is the ability of a system to withstand component failure. For example if the network goes down for 20 seconds then comes back the system should be able to recover and continue functioning.

\paragraph{Usability}
Usability only exists with regard to functionality and refers to the ease of use for a given function. For example a function of an ATM machine is to dispense cash as requested. Placing common amounts on the screen for selection, such as twenty, fourty, and one hundred etc., does not impact the function of the ATM but addresses the Usability of the function.

\paragraph{Efficiency}
This characteristic deals with the system resources used when providing the intended functionality such as disk space, memory, network bandwidth.
It tries to reach compromise between resource utilization and system performance qualities. A hit in efficiency could lead to deteriorated usability quality in a system.

\paragraph{Maintainability}
The ability to identify and fix a fault within a software component is what the maintainability characteristic addresses. Maintainability is impacted by code readability or complexity as well as modularization. Anything that helps with identifying the cause of a fault and then fixing the fault is the concern of maintainability.

\paragraph{Portability}
This characteristic refers to how well the software can adopt to changes in its environment or with its requirements. 