\subsection{Sprint Planning}
	Sprint 0 is planned to be an introductory phase of this project and also the beginning of the development process. During this sprint, team focused on making decisions about technologies that will be used, studying and getting familiar with the assigned problem. The focus was on choice of mobile platform, development process and development of first demo application. One of the important part of this sprint was also field study. Team members got familiar with species observation and principles used for adding new data to customers web application.\newline
	First demo version should consist of simple user interface and some basic functionalities for transition between different views across the menu. Other advanced features, like auto-complete and communication with database will be developed in following sprints.
	
	\subsubsection{Expected results}
	This sprint should provide significant insight into assigned problem and methods for their resolution. Preliminary study is very important part of this sprint. Also, first demo version should be provided, and all important decisions about technical and logical aspect of the project should be made.
	
	\subsubsection{Duration}
	Start of Sprint 0 is September 4th, and it will last until September 12th (week 36). During this sprint, field study is scheduled for September 5th. Customer meeting is on the same day, and advisor meeting is on September 6th.
	
	\input{sprints/ui}
	
\subsection{Customer Feedback}
	After completion of this sprint, and before the beginning of sprint 1, a meeting with the customer was held on September 13th. The team presented conclusions obtained on preliminary study, and also first demo version and the graphical user interface made for this application. Customer agreed on our choices and application design, and also gave some useful suggestions about colour plan and some other issues. PhoneGap proved to be a good choice for development, and customers requirement for cross-platform solution will be satisfied.\newline
	As requested on the customer meeting, the next sprint should focus on auto-completion of species names while making new observation. The team suggested some new tasks for the next sprint, like making local storage for data collected and remembering data during observation, but after a discussion the customer decided priority be given to auto-complete functionality , and to leave development of local storage for next sprint.
	
\subsection{Evaluation}
	This shorter, but not less important sprint provided very valuable information and a lot of decisions have been made that will continue to guide the rest of the development process. First of all, the team got good background during preliminary study. A lot of important issues were discussed in detail, such as development environment, programming and scripting languages, field study etc. All members were involved in this discussions, including both the advisor and the customer. This sprint already saw some programming, but documenting the preliminary study was very important part as well.\newline
	Customer agreed with most of our suggestions, and gave us guidelines for further planing and developing. First demo version is very good, even more than what the customer expected at this phase of the development process.\newline
	Documentation was written by the whole team, and so progress was very satisfactory. However, documenting a lot of things in a short time led to lower document quality. After consultation with the advisor, it was decided that a lot of key changes should be made in next sprint, and the document should be completely reorganized.
