\subsection{Programming and Scripting Language}
It is only natural that developers have a taste for different languages or
learn a new one for as a project in software development. Most of the time,
scripting languages is used for developing Mobile Apps. Mobile applications
can be developed using one or a combination of C, C++, Java, HTML, CSS or JavaScript.

\subsubsection{Native languages}
Most mobile platforms comes with their own preferred programming language. iOS is developed in Objective-C and Android in Java. This requires developers to learn a new language when creating applications for new mobile platforms.

\subsubsection{HTML5}
HTML5 is the fifth revision of the language of the World Wide Web, HTML.
 HTML5 is still in an actively changing draft from. Few browsers full
 support it yet. HTML5 is a new revolution for web application development.
 The design of HTML5 tends to adopt the all the functionalities provided
 by CCS3, JS and HTML.  Offline storage, real-time communication, hardware
 access, better graphics and multimedia content rendition are going to be
 some of the exciting features in the new version.

 \subsubsection{JavaScript}
 JavaScript is the scripting language of the web.
 It is used by web site developers to add better
 functionality, interactivity, communication with the
 server, and for input validation. It also provides developers
 with programming feature. JavaScript is supported by most of
 the popular internet browsers such as Internet Explorer, Firefox,
 Chrome, Opera and Safari.

 \subsubsection{CSS3}
 CSS3 is the third version of the web content formatting scripting language,
 designed by w3c.It removes the formatting features from HTML files and
 stores them a in a separate CSS file.
Developers can define, display and make their interfaces as appealing
as possible using the features of CSS.
CSS is a well-developed standard on the web, and its features are supported across all mobile browsers. CSS3 comes with new features designed to simplify and expand the possibilities designers have when designing web applications.

\subsubsection{jQuery Mobile}
This is a cross-platform and cross-device framework with which one can write
a mobile application capable of running on anyone of the popular mobile platforms.
jQuery is fit for developing applications with touch input, requiring
less processing power and  makes this possible through a lightweight code
built with progressive enhancement and flexibility in mind.

In addition, our customer has previous experience using this framework, and has provided us with a custom built CSS designed for Artsdatabanken. This will enable us to easily conform to design guidelines set by Artsdatabanken.

\subsubsection{Summary}
While programming native applications creates a faster, more user friendly experience, the domain knowledge necessary to test and deliver these applications would take a lot of effort in our group, which would mean we would spend more time learning new programming languages then fulfilling the requirement specification. However, everyone in the group has little to a lot of knowledge making applications using HTML5, CSS3 and javascript. We chose a development framework based on this previous experience. 

Additionally, the customer's requirement was to build an application that is capable of running on multiple platforms. PhoneGap currently supports up to 5 platforms in addition to being open source and using a well known web technology to author the applications and later compile them into native applications. PhoneGap has also been getting recognitions by the likes of established technology companies such as Adobe systems.  Adobe systems has officially integrated PhoneGap in its 5.5 version of Creative suite. While Titanium is a cross platform framework, it only supports Android and iOS. Corona supports only Android and iOS, it is not free and its focus is multimedia rich content and graphics.

 

