\subsection{Functional Requirements}
The functional requirements are listed in this section.
They are meant as a short description of each requirement,
and are further elaborated by the use cases.
This is a dynamic list and will be updated during the project work if the customer wants more from the application.

\subsubsection{Priority}
The priorities are set according to the following description.
\begin{itemize}
	 \item H(High) - These requirements are essential for the prototype to work satisfactorily. These requirements will be prioritized first.
	\item M(Medium) - These requirements are important for the prototype to work satisfactorily. They are important, but not critical for the prototype.
	\item L(Low) - These requirements are not important for the prototype. They are "nice to have", but will be implemented last.
\end{itemize}

\subsubsection{Complexity}
The complexities are set according to the following description.
\begin{itemize}
	\item H(High) - These requirements are hard to do, and will take a lot of time to implement.
	\item M(Medium) - These requirements are possible, but will take some time to implement.
	\item L(Low) - These requirements are easy, and can be implemented in a short time frame.
\end{itemize}

\begin{table}[h!]
	\begin{tabular}[t]{|l|p{0.5\textwidth}|l|l|p{0.15\textwidth}|}\hline
	\bf ID&\bf Requirement& \bf Priority& \bf Complexity\\\hline
	F1&User must be able to create a new observation &High&Medium\\\hline
	F2&User must be able to add more information to a species that has been added to the observation (see use case for details) 	&High&Low\\\hline
	F3&User must be able to add more species to an observation &High&Low\\\hline
	F4&User must be able to export stored observations so they can be uploaded to Artsdatabanken later &High&High\\\hline
	F5&User must be able to take a picture with the device's camera &Medium&Medium\\\hline
	F6&User must be able to view observations that are stored on the device &Low&Medium\\\hline
	F7&User must be able to edit observations that are stored on the device &Low&Low\\\hline
	F8&User must be able to update the local database of species and locations &Low&Medium\\\hline
	F9&An observation must contain GPS coordinates of where it was created. &Medium&Medium\\\hline
	F10&When typing in an observation the application must provide auto-complete facility for that. &Medium&Medium\\\hline
	\end{tabular}
	\caption{Functional requirements}
	\label{funcreqs}
\end{table}
