\section{Abstract}

Motivation, problem statement, approach, results and conclusions

\paragraph{Motivation}
Artsdatabanken, an organization under the Norwegian Department of Education has
long needed a mobile application for species observation. Observers in the field
still use a paper notebook to do observations, and are requesting a simpler and
more effective means to log and register their findings with Artsdatabanken.

\paragraph{Problem statement}
Our task was to develop a cross-platform mobile application that could simplify
registration of species, with automatic gathering of information such as GPS and
pictures, and provide a means to easily register this with Artsdatabankens
systems. The system should replace the old paper notebook, work on mobile
devices such as the iPhone, iPad and Android devices, and reduce the time needed
to register your observations online.

In addition to this, we were tasked with performing research into different
cross-compiling frameworks, and draw a conclusion about which framework worked
the best. We would also evaluate this framework throughout our process to see if
using such a framework was viable as a means to develop cross-platform
applications.

\paragraph{Approach}
Our approach consisted of performing a thorough study of frameworks and the
method of species observations. Amongst other things, we performed a field study
at Artsdatabanken about species observation, and we held workshops discussing
the features of the application. 

The application was developed using the PhoneGap framework, and we focused
primarily on the Android platform. We focused a lot on testing, and used
Test-Driven Development, in addition to performing a usability test of the
application.

The group also established industry-proven quality assurance, and used an agile
methodology based on SCRUM for the project. 

\paragraph{Results}
The final application should work on all mobile devices, but remain untested for
other platforms than Android because of the lack of hardware for testing. The
application is completely programmed in PhoneGap, using jQuery Mobile as the
interface framework.

Our usability testing revealed that... TODO

\paragraph{Conclusion}
TODO


Artsdatabanken is a organization under the Department of Education that is
responsible for species naming and observations. They’ve currently got an online
system for registering such observations and are now looking for an interface
usable on mobile devices.

By observing users we’ve collected knowledge of the process of such
observations, how they are conducted and how they are recorded. An observation
starts off with a person identifying species at a location and noting them down,
then additional details are recorded as well if desirable. Usually in a
notebook, and the later on entered manually on a website. We intend to replace
this notebook with a mobile application to make this process easier and faster,
and also to make it more approachable for new users of the services of
Artsdatabanken.

We developed the application using the cross-compiling framework Phonegap. This
framework utilizes HTML5, CSS3 and JavaScript to develop applications that live
in the browser of the phone. The application itself helps the users create
observations and exporting them for easy upload to Artsdatabankens service. 
