\subsection{Mobile technologies}
The mobile technology field has seen an explosive growth in terms of end user adoption, market penetration, and an ever changing introduction of devices, hardware terminals, platforms, services and portability. Mobile technology has made the current form of computing, where a worker sits in front of a stationary device, less and less appealing. Currently, mobile technology and services providers are in a fierce war for all sorts of reasons, from patent to platform to hardware dominance. The three most iconic feature of a mobile technology are communication(being able to connect wireless), mobility(being able to change from network to network seamlessly), and portability(being able to take the device wherever the work process requires it).
\subsubsection{Mobile platform}

\paragraph{\bf{Android}}

	Android is an operating system developed for a variety of mobile devices.
	It is based on the linux kernel, and provides a developer-friendly
	framework for app development (subset of Java, Dalvik virtual machine).
	Most of it's code is released under the Apache Licence, a free software
	licence.

	Android was listed as the best-selling smartphone platform worldwide in Q4
	2010 by Canalys. \cite{wiki:android}

	\subparagraph{Pros}
		\begin{itemize}
			\item Can be developed using any major operating system (linux, windows, ...)
			\item Android devices can be emulated (AVD). This allows for testing on
			different screen sizes, etc.
			\item Developer-friendly
			\item Open source
		\end{itemize}

	\subparagraph{Cons}
		\begin{itemize}
			\item Apps developed for Android will not run on iOS or Windows phones
		\end{itemize}

\paragraph{\bf{iOS}}

	iOS is Apple's mobile operating system, originally developed for the
	iPhone. Apple does not license iOS for third-party hardware.

	\subparagraph{Pros}
	\begin{itemize}
		\item Uniform screen size over most iPhone devices
		\item Design guidelines
	\end{itemize}

	\subparagraph{Cons}
		\begin{itemize}
			\item Closed and proprietary
			\item Apple hardware and software is required to develop iOS apps
			\item Requires a yearly subscription to distribute apps developed
			for iOS
			\item GPL and other free software licenses can conflict with
			Apple's terms
			\item Design guidelines can create artificial limitations
			\item Apps developed for iOS will only run on Apple products
		\end{itemize}

\input{prestudy/mobile_technology/phonegap}
\input{prestudy/mobile_technology/native}

