\subsection{Conventions}

\subsubsection{LaTeX}
All documentation regarding the project should be written in LaTeX. We will
follow the standard article format included by LaTeX, printed with a standard
a4paper.

\paragraph{Encoding}
The encoding of the document will be UTF-8, so that we avoid encoding errors
when we compile the document.

\paragraph{Tables and figures}
Tables and figures will be printed in landscape format before the table is
broken down into several pages.
This keeps the formatting of the tables consistent and readable for as long as
possible. A table should never exceed the maximum textwidth of the page. The
same rule applies for figures.

\paragraph{References}
All references should contain a short and descriptive name, and a category, so
that all articles from e.g. Wikipedia are referenced wiki:article, and all
references about phonegap are referenced phonegap:page.

\subsubsection{JavaScript}

JavaScript code should never be embedded in HTML files. Script tags should be
placed as late in the body as possible. \cite{crockford:code}

\paragraph{Line length and indentation} \hspace{1mm}

Tabs should be used for indentation.
Lines should not be longer than 80 characters.

\paragraph{Comments and variable names} \hspace{1mm}

Comments should be kept at a minimum. They are disruptive to the code and
usually outdated. Focus should be on writing good code instead of writing comments. Comments can be used to
clarify code that is not self-explanatory or to warn about issues like
framework bugs or weak code. All developers should have on mind that the code should already
be documented by written tests, before implementing the feature.

Variables should have descriptive names. It is better to try to find good names before
resorting to comments.

To indicate that a variable refers to jQuery objects developers sometimes
prefix it with \$. This team will not use this convention, it makes it hard to
spot actual jQuery calls.

\paragraph{Declarations} \hspace{1mm}

Variables should always be declared, this will prevent conflicts with globals.

Functions should be declared as follows:

\begin{lstlisting}
	function somename(...) {
		...
	}

	var somename = function(...) {
		...
	}
\end{lstlisting}

Space should never be placed between the function name and the first parenthesis.

\paragraph{Statements} \hspace{1mm}

If statements should have the following form (notice that the else statement is
not on the same line as the closing curly brace):

\begin{lstlisting}
	if (condition) {
		statements
	}
	else {
		statements
	}
\end{lstlisting}

A switch statement should have the following form:

\begin{lstlisting}
	switch (expression) {
		case condition:
			statements
			break;
		... more case ...
		default:
			statements
	}
\end{lstlisting}
