\subsection{The application}
	
    \subsubsection{Deliverables}
    %ok
    When the group set out on this project, we were all well aware that we were very likely to meet challenges along the way. To plan for the worst and take pre-emptive action, we sat together and designed the project plan, a risk analysis and mitigation strategy---should anything goes wrong, a mutual agreement on implementation technology, a decision on time schedule and other key administrative routines.

%ok
    Planning administrative and procedural routines ahead of any actual work contributed considerably to keep everyone on the same page. We actually managed to finish 90 percent of the requirements we elicited together with requirements the customer approved and accepted.

%ok?
    The group thought it would be best to let people work and focus in the areas they felt the most confident, so we had those who felt the most comfortable programming focused on the programming part of the project, and so on. This we felt contributed to the overall quality of our final product. 
   % To realize the requirements from paper work to a actual implementation, people who invested so much time in the programming department worked day and night relentlessly to implement all the requirements on paper, despite the fact that each member has a responsibility in other courses as well. And group member whose focus was on documentation and administration did a superb job to rearrange requirement specification accordingly, document sprints, handle status reports, and document implementations.

%ok
    The collaboration and common understanding between the group members enabled us to finish a beta application version early and send it for testing to our customer, the result of which will be presented in another section.

%ok
    According to our agreement with our customer, the application was to be delivered as a prototype with certain functionalities being non-negotiable part of the prototyping. We managed to implement all the non-negotiable functionalities and test them. In our opinion, it is safe to say that we completed this application quite successfully, with 90 percent of our functional requirements implemented. Growing time pressure and the relatively high complexity and low priority of this final requirement caused us to decide to document an implementation strategy for it and leave it at that. The customer agreed that this was the better approach.

    %Overall, our application was delivered as specified by the customer and the group has tried to do everything possible to conform to the customer's requirements and meet his expectation.
    
	\subsubsection{Final version and deployment}
The application we delivered to the customer is only a prototype. It needs a certain degree of performance tuning for general public use, and also to bring it up to a professional par.

The final version of the application we published to our customer does the functionalities specified in the requirements. The application is a cross-platform mobile application that can be run on Android and iOS based mobile devices. We have actually not been able to test it on i-family devices, due to the fact that none of us had such a device and the assumption was for the customer to provide an i-family testing device. But the customer failed to provide the device and recommended we focus our testing effort on Android based devices and forgo iOS based testing.

%But the application testing on Android device went well as expected and we carried out an actual test on actual users of our customers.


	\subsubsection{Customer response}
The customer was made to be involved actively in the process and he was consulted from the beginning to the end of the project. We made sure he knew what was going on in the technology, mode of implementation and our schedule to remotely eliminate unexpected surprises.

All along, the customer's feedback was positive and encouraging. At this point we are unaware of anything that might have gone against the expectations of the customer.
We have included his suggestions and recommendations and any changes and modifications took place with his opinions factored in.

We believe that we managed to satisfy our customer's expectations and that he had no reservations with our final prototype.
	%\subsubsection{Application deployment}
	


