\subsection{People involved and the course}
	\subsubsection{Customer}
One of the things that have been very helpful in this course was having the
customer we had. He went an extra mile to make sure we had a good understanding
of what his requirements were, he invested his time to train some of our
group members the trickier system of taxonomy - a scientific species naming
system, and the company organized a field work for us so we could experience the
task in the requirements first hand.

Our customer knew exactly what he wanted, and his requirements were already well
thought out. He gave us a green light as to how we approached his requirements
as long as we met his expectations. He gave us the independence to test our
ideas, select our own technology and methodology, only intervening when
necessary and explicitly requested. In addition to that, he replied to our
emails on time with the necessary information and attended our meetings
consistently as planned.

The customer also had a deeper understanding of their existing system, including
the weaknesses, strengths and the semantics of the business areas of
Artsdatabanken. He provided helpful insight into exploiting already implemented
backend systems, such as the open API for species offered by Artsdatabanken.

Since we had to do every form of communication in English, and none of us were
native speakers of the language, language was one of the things we had to take
into consideration to guarantee reliable and clearer understanding between
everyone involved. The customer mastered the English language well and our
communications took place without any difficulty.

We held our customer meeting at the beginning of every sprint and he
actively promoted ideas he seemed to like and suggested improvements.  His
guidance was very helpful to avoid misguided approaches and fuzzy implementation
procedures. In addition he motivated us greatly for the project, and gave us
helpful insights into the documentation part of the project as well.

	\subsubsection{Advisor}
We were lucky to have a responsible advisor whose intuitive advice has
enormously helped us stay on track, be goal oriented, keep up with ours and our
customers expectations and on the amount of work to be done each week. His
advices were very honest, professional and comprehensive. He spoke his mind and
we used the honest remarks to make improvements on our work strategy and
progress. He attended all our meetings on time and his communication in English
was excellent.

The weekly advisor meetings have been key reference points to gauge our
progress, document quality and milestone settings. It also helped us stay
motivated throughout the project, and his experience helped us avoid the biggest
pitfalls of the project.

\subsubsection{Team}
  The team consists of 7 fourth year students of the Norwegian University of
  Science and Technology. Five student are enrolled in the Master of Computer
  Science program, and two are enrolled in the International Master in Computer
  Science. We feel that the group dynamics has worked out well, and our project
  has benefited greatly from that. A huge part of this is the excellent spoken
  and written English of the group, which has proved to be invaluable in good
  communication and cooperation between the group members.

  All group members feel that the workload has been evenly distributed, and we
  have carefully taken into consideration other classes and distributed work
  accordingly, so that no one fell behind in other classes because of the
  project. This has proved to be key in the success of the project, because
  motivation was high throughout the entire process, making us more effective in
  completing our weekly goals.

\subsubsection{The course}

   This course is special in that it required not only special skills
   in computer science but also a string of skills that we had garnered all
   along our educational stay in the university. This course helped us test our
   fitness for a professional software engineering atmosphere. We have been able
   to employ our skills from requirements elicitation and engineering to
   software design and technical writing. The course had such an extensive
   coverage of subjects in computer science it gave us a means to
   summarize and reinforce our previous knowledge in information systems.

   The course had its own share of challenges. Managing groups, customer
   communication, advisor guidelines and the actual work itself was something
   which tested our skill and patience. At times, we have found the course work
    intimidating and more than what we were used to and expected. In our case,
   we were fortunate to have the right number of group members to conduct our
   business without interruptions. We experienced that even though some group
   members fell ill or were busy with other courses, we still managed to
   complete our workload for each week. This was due to good distribution of
   human resources and the generally high motivation of the group.
   
   The support the course gets from advisor in the form of weekly meetings, the
   compendiums at the beginning of the course, and reserves of previous projects
   for reference has helped us cope with the challenges. We feel that the course
   has helped motivate us to continue our work in this field, and we have gained
   a lot of experience in handling internal and external sources of conflict
   throughout the project.
