\subsection{Programming and Scripting Language}
It is only natural that developers have a taste for different languages or
learn a new one for as a project in software development. Most of the time,
scripting languages is used for developing Mobile Apps. Mobile applications
can be developed using one or a combination C, C++, Java, HTML, CSS, JavaScript.
\paragraph{HTML5}

HTML5 is the fifth revision of the language of the World Wide Web, HTML.
 HTML5 is still in an actively changing draft from. Few browsers full
 support it yet. HTML5 is a new revolution for web application development.
 The design of HTML5 tends to adopt the all the functionalities provided
 by CCS3, JS and HTML.  Offline storage, real-time communication, hardware
 access, better graphics and multimedia content rendition are going to be
 some of the exciting features in the new version.

 \paragraph{JavaScript}\\
 JavaScript is the scripting language of the web.
 It is used by web site developers to add better
 functionality, interactivity, communication with the
 server, and for input validation. It also provides developers
 with programming feature. JavaScript is supported by most of
 the popular internet browsers such as Internet Explorer, Firefox,
 Chrome, Opera and Safari.
 \paragraph{CSS3}\\
 CSS3 is the third version of the web content formatting scripting language,
 designed by w3C.It removes the formatting features from HTML files and
 stores them a in a separate CSS file.
Developers can define, display and make their interfaces as appealing
as possible using the features of CSS.
\paragraph{jQuery Mobile}\\
This is a cross-platform and cross-device framework with which one can write
a mobile application capable of running on anyone of the popular mobile platforms.
jQuery is fit for developing applications with touch input, requiring
less processing power and  makes this possible through a lightweight code
built with progressive enhancement and flexibility in mind.


