\subsection{Tech comparison}

\subsubsection{Android}

	Android is an operating system developed for a variety of mobile devices.
	It is based on the linux kernel, and provides a developer-friendly
	framework for app development (subset of Java, Dalvik virtual machine).
	Most of it's code is released under the Apache Licence, a free software
	licence.

	Android was listed as the best-selling smartphone platform worldwide in Q4
	2010 by Canalys. \cite{wiki:android}

	\paragraph{Pros}
		\begin{itemize}
			\item Can be developed using any major operating system (linux, windows, ...)
			\item Android devices can be emulated (AVD). This allows for testing on
			different screen sizes, etc.
			\item Developer-friendly
			\item Open source
		\end{itemize}

	\paragraph{Cons}
		\begin{itemize}
			\item Apps developed for Android will not run on iOS or Windows phones
		\end{itemize}

\subsubsection{iOS}

	iOS is Apple's mobile operating system, originally developed for the
	iPhone. Apple does not license iOS for third-party hardware.

	\paragraph{Cons}
		\begin{itemize}
			\item Closed and proprietary
			\item Apple hardware and software is required to develop iOS apps
			\item Requires a yearly subscription to distribute apps developed
			for iOS
			\item Apple maintains the right to remotely disable or delete apps
			at will
			\item GPL and other free software licenses can conflict with
			Apple's terms
			\item Problematic programming language, Objective-C (lacking garbage collector)
		\end{itemize}

	\begin{itemize}
		\item iOs development requires
			\begin{itemize}
				\item Macintosh running Mac OSX
				\item iFamily device for testing
			\end{itemize}
	\end{itemize}

\input{prestudy/tech_comparison/phonegap}
\input{prestudy/tech_comparison/native}
