\subsection{Quality Assurance}

This section contains routines that should be followed to ensure the
quality of the product and its report. In a bid to incorporate quality ensuring procedures, the group will try to execute the development tasks in line with internationally accepted standards recommendations documents such as ISO9126 and ISO9100

\paragraph{ISO9126}
ISO9126 is a document from the international organization for standardization that recommends software qualities be checked against six core characteristics, which are described in short below and will be used as reference point for quality assurance reminders in this project\cite{iso:9126}.

\begin{itemize}
		\item Functionality - make sure the functionalities are those functionalities that satisfy the stated or implied needs.
		\item Reliability - make sure the software is capable of maintaining its level of performance under a specified condition in a specified period of time.
		\item Usability - the level of effort to use the system and assessment by a stated set of users.
		\item Efficiency - The level of performance versus the amount of resource applied under a specified condition.
        \item Maintainability - The level of effort required to make a specified modifications.
        \item Portability - The ability of the software to be able to be deployed or be transferred from one environment to another.
\end{itemize}


\subsubsection{Overall Group Dynamics}

All communication will be done in English.
Monday through Thursday every week there will be scrum stand-up at 0915 at Drivhuset.
Documentation written should be proofread by at least one of the other group members
to assure good grammar and avoid typographical errors.
Every meeting starts with a meeting agenda and notes for the meeting minutes will be
written for all meetings and distributed.

\subsubsection{Customer Relations and Meetings}

There will be a demo for the customer on every customer meeting to let them
know how far along the project is and to catch misunderstandings or direction changes early on.
The customer will receive the meeting minutes after every meeting and approve them,
if there is no response within 48 hours they are regarded as approved.

\subsubsection{Advisor Relations and Meetings}

There will be a meeting with the Advisor every week, any information that the advisor
should comment on should be submitted to him before 1400 the day prior to the meeting.
On a regular basis this includes: project status, project plan, summary of last weeks
meeting minutes and an hour sheet for group members, this should preferably be included in one document.
Always include group number when contacting the advisor.
