\begin{landscape}
\subsection{Risk analysis}

\centering
\begin{longtable}{| p{0.4cm} | p{4cm} | p{4cm} | p{2cm} | p{4cm} | p{1cm} | p{4cm} |}
	\hline
		\multicolumn{1}{|c|}{ Id}   &
        \multicolumn{1}{c|}{ Project Risk}  &
		\multicolumn{1}{c|}{ Risk indicators}  &
		\multicolumn{1}{c|}{ Likelihood} &
		\multicolumn{1}{c|}{ Effect} &
		\multicolumn{1}{c|}{ Impact} &
		\multicolumn{1}{c|}{ Mitigation} \\
		\hline \hline
	\endhead

	\newcounter{riskId}

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Participance i voluntary associations
		&
		\centering L &
		Work delay and inconvenience. Meeting agendas might me late. &
		\centering M &
		The group leader should distribute work accordingly. Members will notify 24 hours beforehand. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Customer changing their requirements &
		If the customer have a lot of requirements, but can’t be decisive &
		\centering M &
		Slow progress, uncertainty about work requirements and project state &
		\centering  M &
		Pinpoint requirements early, agree upon a written requirements
		specification. Getting one clear product owner we can ask for
		directions.  Communication with customer. Ask the advisor for help.
		Customer approves the requirements we write, and the meeting minutes.
		\\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Time spent on work unrelated to this project &
		Risk Indicators: &
		\centering M &
		Less time for project &
		\centering M & 
		Prioritize this project when possible \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        One of the group members is absent for a longer period of time (>2 days) &
		& \centering H &
		Work delay and inconvenience. &
		\centering  L &
		Distribute work accordingly. Extend period until delivery if possible.
		Group members can communicate via email. Absent group member can do
		simple tasks. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
		One of the group members may be overloaded with work from project and other
		classes &
		The person is stressed, might be sick for a longer period of time, less
		quality of work, inconsistent work pattern &
		\centering L &
		Higher workload for other group members. Might lead to the same risk. &
		\centering  L & Distribute work to other members while this member is
		overloaded, if this is not possible, minimize requirements with the
		customer. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Underestimated workload or complexity task. &
		Slow progress. Quality issues. &
		\centering  L &
		Incomplete product, Customer dissatisfaction. Bad grades. A big
		workload at the end of the project. &
		\centering  H &
		Research into problem domain and coding frameworks. Figure out
		group member skills and plan accordingly. Create a skill matrix. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Missing project deliverable &
		High workload, slow progress. Repeated failure to deliver the
		deliverables on time. &
		\centering  L &
		Bad grade and customer dissatisfaction &
		\centering H &
		Re-plan the project. Make the deliverables realistic to complete.
		Realistic deliverable goals. Discuss with the customer about removing
		some deliverables. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Customer doesn’t provide a Mac for testing iOS application. &
		& \centering H &
		The finished product will not be tested on iOS, and we cannot deploy
		our application to iOS App store. &
		\centering  M &
		Tell the customer we cannot provide the application for the iOS
		platform due to lack of hardware. Get to an agreement with the customer
		over this. Find a Mac from a different source than the client. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
		Export feature not working correctly or lacking in finished product. &
		Complex code, bad communication with database, failures during
		testing. &
		\centering  M &
		Customer dissatisfaction, usability problem &
		\centering H &
		Prioritize the export feature early, start work on it as soon as
		possible. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
		One of the group members experience hardware failure or loss of data &
		& \centering L &
		Losing important data, goals not being made, higher workload for the
		rest of the group &
		\centering M &
		Commit to github often, or use Google Docs as a backup. Can use NTNUs
		computers or backup computers provided by the project group. \\
	\hline
\caption{Risk analysis}
\end{longtable}

\end{landscape}
