\subsection{Mobile technologies}
The mobile technology field has seen an explosive growth in terms of end user adoption, market penetration, and an ever changing introduction of devices, hardware terminals, platforms, services and portability. Mobile technology has made the current form of computing, where a worker sits in front of a stationary device, is becoming less and less appealing. Currently, mobile technology and services providers are in a fierce war for all sorts of reasons, from patent to platform to hardware dominance. The three most iconic feature a mobile technology are communication—being able to connect wireless, mobility—being able to change from network to network seamlessly, and portability—being able to take the device wherever the work process requires it.
\subsubsection{Mobile platform}

\paragraph{Android}

	Android is an operating system developed for a variety of mobile devices.
	It is based on the linux kernel, and provides a developer-friendly
	framework for app development (subset of Java, Dalvik virtual machine).
	Most of it's code is released under the Apache Licence, a free software
	licence.

	Android was listed as the best-selling smartphone platform worldwide in Q4
	2010 by Canalys. \cite{wiki:android}

	\subparagraph{Pros}
		\begin{itemize}
			\item Can be developed using any major operating system (linux, windows, ...)
			\item Android devices can be emulated (AVD). This allows for testing on
			different screen sizes, etc.
			\item Developer-friendly
			\item Open source
		\end{itemize}

	\subparagraph{Cons}
		\begin{itemize}
			\item Apps developed for Android will not run on iOS or Windows phones
		\end{itemize}

\paragraph{iOS}

	iOS is Apple's mobile operating system, originally developed for the
	iPhone. Apple does not license iOS for third-party hardware.

	\subparagraph{Pros}
	\begin{itemize}
		\item Uniform screen size over most iPhone devices
		\item Design guidelines
	\end{itemize}

	\subparagraph{Cons}
		\begin{itemize}
			\item Closed and proprietary
			\item Apple hardware and software is required to develop iOS apps
			\item Requires a yearly subscription to distribute apps developed
			for iOS
			\item Apple maintains the right to remotely disable or delete apps
			at will
			\item GPL and other free software licenses can conflict with
			Apple's terms
			\item Problematic programming language, Objective-C (lacking garbage collector)
			\item Design guidelines can create artificial limitations
			\item Apps developed for iOS will only run on Apple products
		\end{itemize}

\input{prestudy/mobile_technology/phonegap}
\input{prestudy/mobile_technology/native}

\subsubsection{Mobile Networks}

\paragraph{GSM/ Global System for Mobile Communication}
GSM is the world’s most popular and widespread system for mobile communication. Since its pioneer in 1993 in Norway, it has now spread in 219 countries in the world. Almost all mobile handsets are fitted with GSM. It is an open digital cellular technology used to transmit voice and data services.
\paragraph{GPRS/General Packet Radio Service}
GPRS is an extension of GSM as a 2.5 generation technology; it is mainly used for wireless data services. GPRS service costs are in terms of the amount of data transferred. It offers a band width of up to 40kbit/s.
\paragraph{UMTS/ Universal Mobile Telecommunications System}
UMTS is a 3G broadband packet based transmission system for mobile handsets. It is capable of providing more than 1Mb/s bandwidth for transferring text, multimedia content, online streaming and other bandwidth demanding services. It is considered a broadband technology for mobile phones.
\paragraph{Wireless hotspot, Bluetooth, Infrared and Access point}

\subsubsection{Mobile Services and functions}


\paragraph{SMS and MMS}
SMS and MMS are two other ways of communicating using a mobile handset. SMS enables one to send a text message of up to 160 characters. SMS is being used for money transfer, personal communication, and disaster relief. While MMS is allows one to exchange multimedia messages composed of a text message, pictures, video, animation or audio, but MMS is mostly a premium service than SMS due to its network bandwidth requirements.

\paragraph{Mobile Positioning Systems}
The most well-known navigational system in the world is the Global Positioning system, which is an implemented by the US’s Department of Defense.  The service is based on a constellation of between 24 to 32 medium earth orbit satellites transmitting signals that will help a mobile handset decide the approximate location using Latitude and Longitude coordinates on the surface of the Earth.

\paragraph{Multimedia Tools}

In recent years, the mobile handset has witnessed a major change in hardware capability and functionality richness of both the hardware and the software component in the form of smartphones. Smartphones are becoming more and closer to handheld computers. Smartphones are capable of recording audio, video or taking pictures and developing a rich digital content, which will give extra hand in the productivity of a mobile worker. Notable feature of a multimedia tool on a smartphone are the camera, audio and video recorder.

