\begin{landscape}
\section{Risk analysis}

\centering
\begin{longtable}{| p{0.4cm} | p{4cm} | p{4cm} | p{2cm} | p{4cm} | p{1cm} | p{4cm} |}
	\hline
		\multicolumn{1}{|c|}{ Id}   &
        \multicolumn{1}{c|}{ Project Risk}  &
		\multicolumn{1}{c|}{ Risk indicators}  &
		\multicolumn{1}{c|}{ Likelihood} &
		\multicolumn{1}{c|}{ Effect} &
		\multicolumn{1}{c|}{ Impact} &
		\multicolumn{1}{c|}{ Mitigation} \\
		\hline \hline
	\endhead

	\newcounter{riskId}

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Muhsin is involved with a voluntary association called NORKUF &
		&
		\centering L &
		Work delay and inconvenience &
		\centering M &
		Distribute work accordingly. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Dag-Inge is involved with a voluntary association called ISFiT &
		& \centering M &
		Work delay and inconvenience. Meeting agendas might me late. &
		\centering  M &
		Yonathan will write meeting agendas. Dag-Inge will notify 24 hours beforehand. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Customer changing their requirements &
		If the customer have a lot of requirements, but can’t be decisive &
		\centering M &
		Work delay and inconvenience. Meeting agendas might me late. &
		\centering  M &
		Yonathan will write meeting agendas. Dag-Inge will notify 24 hours beforehand. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Stian will do some web development on the side (work) &
		Risk Indicators: &
		\centering M &
		Less time for project &
		\centering M & \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        One of the group members is absent for a longer period of time (>2 days) &
		& \centering H &
		Work delay and inconvenience. &
		\centering  L &
		Distribute work accordingly. Extend period until delivery if possible. Group members can communicate via email. Absent group member can do simple tasks. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        One of the group members is overloaded with work from project and other classes &
		The person is stressed, might be sick for a longer period of time, less quality of work, inconsistent work pattern &
		\centering L &
		Higher workload for other group members. Might lead to the same risk. &
		\centering  L & Distribute work to other members while this member is overloaded, if this is not possible, minimize requirements with the customer. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Unclear customer requirements &
		Different opinions between product owners. Lack of progress. Unclear sprint log. Unclear prioritization. &
		\centering  M &
		Changing requirements, incomplete product. Customer dissatisfaction. Bad grades. &
		\centering  H &
		Getting one clear product owner we can ask for directions. Communication with customer. Ask the advisor for help. Customer approves the requirements we write, and the meeting minutes. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Underestimate workload. Underestimate the complexity of the task. &
		Slow progress. Many problems with the product. &
		\centering  L &
		Incomplete product, Customer dissatisfaction. Bad grades. A big workload at the end of the project. &
		\centering  H &
		Good research into problem domain and coding frameworks. Figure out group member skills and plan accordingly. Create a skill matrix. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Missing project deliverable &
		High workload, slow progress. Repeated failure to deliver the deliverables on time. &
		\centering  L &
		Bad grade and customer dissatisfaction. Total collapse of the project &
		\centering H &
		Replan the project. Make the deliverables realistic to complete. realistic delivarable goals. Discuss with the customer about removing some deliverables. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Customer doesn’t provide a Mac for testing iOS application. &
		& \centering H &
		The finished product will not be tested on iOS, and we cannot deploy our application to iOS App store. &
		\centering  M &
		Tell the customer we cannot provide the application for the iOS platform due to lack of hardware. Get to an agreement with the customer over this. Find a Mac from a different source than the client. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        Export feature not working correctly or lacking in finished product. &
		Complex code, bad communication with database, several failures during testing. &
		\centering  M &
		Customer dissatisfaction, usability problem &
		\centering H &
		Prioritize the export feature early, start work on it as soon as possible. \\
	\hline

	\stepcounter{riskId}
	\centering
		\arabic{riskId} &
        One of the group members experience hardware failure or loss of data &
		& \centering L &
		Loosing important data, goals not being made, higher workload for the rest of the group &
		\centering M &
		Commit to github often, or use Google Docs as a backup. Can use NTNUs computers or backup computers provided by the project group. \\
	\hline
\caption{Risk analysis}
\end{longtable}

\end{landscape}
